### 2022-03-02 paper/paper.tex
benchmark and assoc writeup

% Language selector
\newif\ifEN
\ENtrue % Change to false to export Korean
%\ENfalse

\ifEN
{
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{conjecture}{Conjecture}
}
\else {
\newtheorem{theorem}{정리}
\newtheorem{lemma}{기본정리}
\newtheorem{corollary}{따름정리}
\newtheorem{proposition}{제의}
\theoremstyle{definition}
\newtheorem{example}{예}
\newtheorem{definition}{정의}
\newtheorem{assumption}{가정}
\newtheorem{conjecture}{추측}
}
\fi

%\ifEN {} \else \renewcommand*{\proofname}{증명\@}  \fi

@@

\ifEN{ \title{How to apply to college} }
\else {\title{How to apply to college}} \fi
\author{Max Kapur}
\date{\today}                % Activate to display a given date or no date

@@

\maketitle
\section*{Abstract}
This paper considers the maximization of the expected maximum value of a portfolio of random variables subject to a budget constraint. We refer to this as the optimal college application problem. When each variable's cost, or each college's application fee, is identical, we show that the optimal portfolios are nested in the budget constraint, yielding an exact polynomial-time algorithm. When colleges differ in their application fees, we show that the problem is NP-complete. We provide two dynamic programs for this more general setup. The first produces an exact solution in pseudopolynomial time, and the second yields a fully polynomial-time approximation scheme. 
\pagebreak

\tableofcontents
\pagebreak

\ifEN \section{Introduction}  \else \section{서론} \fi
This paper considers the portfolio optimization problem
%\begin{definition}[Optimal college application portfolio] \label{generalproblemstatement}
\begin{align}
\begin{split}
\text{maximize}\quad & \operatorname{E}\Bigl[\max\bigr\{t_0,
\max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\Bigr] \\
\text{subject to}\quad & \mathcal{X} \subseteq \mathcal{C}, ~~\sum_{j\in \mathcal{X}} g_j \leq H
\end{split}
\end{align}
%\end{definition}
where $\mathcal{C} = \{ 1 \dots m\}$ is an index set, $H$ is a budget parameter, and for $j = 1 \dots m$, $g_j > 0$ is a cost parameter, $Z_j$ is a random, independent Bernoulli variable with probability $f_j \in (0, 1]$, and $t_j  > 0$ is a utility parameter. Without loss of generality, we assume that the $t_j$-values are weakly increasing in $j$, that $0 \leq t_0 \leq t_1$, and that each $g_j \leq H$.

We refer to this problem as the \emph{optimal college application portfolio,} as follows: Consider a college market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. Finally, let $f_j$ denote her probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are probabilistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she gets into within this budget. Her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies.

As Chao (2014) remarked, college application represents a somewhat subtle portfolio optimization problem. Traditional portfolio optimization models weigh the expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Meucci 2005). But college applicants maximize the observed value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the expected utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability is negatively correlated with competitiveness. That is, students  negotiate a tradeoff between highly attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet. Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Chao estimated her model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is possible. Our study pursues a more general solution.

We take special interest in the validity of greedy solution algorithms, such as that that iteratively adds the asset that yields the greatest increase in the objective function until the budget is exhausted.
% Greedy algorithms produce a nested, parametric family of solutions. As Rozanov ...
For certain classes of optimization problems, such as maximizing a submodular set function over a cardinality constraint, the greedy algorithm is known to be a good approximate solution and exact under certain additional assumptions (Fisher et al. 1978). For other problems, notably the binary knapsack problem, the most intuitive greedy algorithm can be made to perform arbitrarily poorly (Vazirani 2001).

We show analogous results for the college application problem: In the special case where each $g_j = 1$, the optimal portfolio satisfy a nestedness property that is equivalent to the validity of the greedy algorithm. As Rozanov and Tamir (2020) remark, the nestedness property is useful not only for obtaining an optimal solution, but in the implementation of an optimal policy under uncertain information. In the United States, many college applications are due at the beginning of November, and it is typical for students to begin working on their applications during the prior summer because colleges increasingly expect students to tailor their essays to the target school. Therefore, students may not know how many schools they can afford to apply to (in terms of both time and monetary costs) until late October. The nestedness property implies that students can prioritize their application strategy by working on applications in the order that they appear in the sequence of optimal application portfolios.

Unfortunately, the nestedness property does not hold in the general case, nor does the greedy algorithm offers any performance guarantee. Instead, we offer a pseudopolynomial-time algorithm that is tractable for typical college market instances, as well as an approximation scheme that produces a $(1 - \varepsilon)$-optimal solution in fully polynomial time.

\subsection{Structure of this paper}
Section \ref{preliminaries} introduces some additional notation and assumptions that can be imposed with trivial loss of generality.

In section \ref{homogappcosts}, we solve the special case where each $g_j = 1$ and $H$ is an integer $h \leq m$. This case mirrors the centralized college application process in Korea, where there is no application fee, but students are allowed to apply to only three schools during the main admissions cycle. We show that an intuitive heuristic is in fact a $1/h$-approximation algorithm. Then, we show that the optimal portfolios are nested in the budget constraint, which yields an exact algorithm that runs in $O(hm)$-time.

@@

\section{Notation and preliminary results} \label{preliminaries}
Before discussing the solution algorithms, we will introduce some additional notation and a few preliminary results that will come in handy.

We refer to the set $\mathcal{X} \subseteq \mathcal{C}$ of schools to which a student applies is called her \emph{application portfolio.} The expected utility the student receives from $\mathcal{X}$ is called its \emph{valuation}. %Let $x$ denote the same encoded as a binary vector, where $x_j=1 \iff j\in \mathcal{X}$ for $j=1\dots m$. 
\begin{definition}[Portfolio valuation function]
$v(\mathcal{X}) =  \operatorname{E}\left[\max\bigr\{t_0,
\max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\right]$.
\end{definition}
It is helpful to define the random variable $X  = \max\{ t_j Z_j : j \in \mathcal{X}\}$ as the utility achieved by the schools in the portfolio, so that when $t_0 = 0$, $v(\mathcal{X}) = \operatorname{E}[X]$. Similar pairs of variables with italic and script names such as $\mathcal{Y}_h$ and $Y_h$ carry an analogous meaning.

@@

\ifEN \section{Homogeneous application costs}  \else \subsection{} \fi \label{homogappcosts}
In this section, we derive a polynomial-time algorithm for the special case in which $g_j = 1$ and $H$ is a constant $h \leq m$. This case is similar to the centralized college admissions process in Korea, where there is no application fee, but by law, students are allowed to apply to no more than $h$ schools. (In the Korean case, $m=202$ and $h=3$.) Applying Theorem \ref{assumetzerozero}, we assume that $t_0 = 0$ unless otherwise noted. Throughout this section, we will call the applicant Alma, and refer to the corresponding optimization problem as Alma's problem.

@@

\ifEN \subsection{Approximation properties of a na\"ive solution}  \else \subsection{모형화} \fi
The expected utility associated with a single school $c_j$ is simply $\operatorname{E}[t_j Z_j] = t_j f_j$. It is therefore tempting to adopt the following strategy, which turns out to be inoptimal.
\begin{definition}[Na\"ive algorithm for Alma’s problem] \label{naivealgorithm}
Apply to the $h$ schools having the highest expected utility $t_j f_j$.
\end{definition}
The basic error of this algorithm is that it maximizes $\operatorname{E}\left[\sum t_j Z_j \right]$ instead of $\operatorname{E}\left[\max \{t_j Z_j\} \right]$. The latter is what Alma is truly concerned with, since in the end she can attend only one school. The following example shows that the na\"ive algorithm can produce a suboptimal solution.
\begin{example}
Suppose $m=3$, $h=2$,  $ t= (70, 80, 90) $, and $f = (0.4, 0.4, 0.3)$. 
%\implies t * f &= (28, 32, 27)
%\begin{align*}
%t &= (70, 80, 90) \\
%f &= (0.4, 0.4, 0.3) \\
%\implies t * f &= (28, 32, 27)
%\end{align*}
Then the na\"ive algorithm picks $\mathcal{T} = \{1, 2\}$ with 
$v(\mathcal{T}) = 70(0.4)(1-0.4) + 80(0.4) = 48.8$.
But $\mathcal{X} = \{2, 3\}$ with
$v(\mathcal{X}) = 80(0.4)(1-0.3) + 90(0.3) = 49.4$
is the optimal solution. 
\end{example}

@@

@@

\ifEN \subsection{The nestedness property}  \else \subsection{풀이} \fi
It turns out that the solution to Alma's problem possesses a special structure: An optimal portfolio of size $h+1$ includes an optimal portfolio of size $h$ as a subset.
% Incl above
%To show this result, we need to introduce some new notation. For an application portfolio $\mathcal{X}$, the random variable $X  = \max\{ t_j Z_j : j \in \mathcal{X}\}$ represents the utility achieved by the portfolio, so that $v(\mathcal{X}) = \operatorname{E}[X]$.

@@

\subsection{Polynomial-time solution}
Applying the result above yields an efficient algorithm for the optimal portfolio: Start with the empty set and add schools one at a time, maximizing $v(\mathcal{X}\cup \{k\})$ at each addition. Sorting $t$ is  $O(m \log m)$.  At each of the $h$ iterations, there are $O(m)$ candidates for $k$, and computing $v(\mathcal{X}\cup \{k\})$ is $O(h)$ using \eqref{closedformportfoliovaluationX}; therefore, the time complexity of this algorithm is $O(h^2 m + m \log m)$. 
%\begin{algorithm}[H] 
%  %\DontPrintSemicolon
%\caption{Optimal portfolio algorithm for Alma’s problem when $h$ is small.} \label{algorithmforsmallh}
%\KwData{Utility values $t \in[0, \infty)^m$, admissions probabilities $f \in [0, 1]^m$, application limit $h \leq m$.}
%Index schools in ascending order by $t$\;
%$\mathcal{X} \gets \O$\;
%\For{$i=1\dots h$}
%{
%    $j \gets \argmax_k\bigl\{v(\mathcal{X}\cup\{k\}) : k \notin \mathcal{X}\bigr\}$\;
%    $\mathcal{X} \gets \mathcal{X}\cup\{j\}$ \;
%}
%\Return{$\mathcal{X}$}
%\end{algorithm}
%
%\begin{theorem}[Validity of Algorithm \ref{algorithmforsmallh}]
%Algorithm \ref{algorithmforsmallh} produces an optimal application portfolio in $O(h^2 m + m \log m)$ time.
%\end{theorem}
%\begin{proof}
%Optimality follows from Theorem \ref{nestedapplication}. Sorting $t$ is  $O(m \log m)$. At each of the $h$ iterations, there are $O(m)$ candidates for $k$, and computing $v(\mathcal{X}\cup \{k\})$ is $O(h)$ using \eqref{closedformportfoliovaluationX}; therefore, the time complexity of the main loop is $O(h^2 m)$. 
%\end{proof}

@@

\subsection{Properties of the optimal portfolios}
The nestedness property implies that Alma's expected utility is a discretely concave function of $h$.

@@

\section{Heterogeneous application costs}  \label{hetappcosts}
In this section, we turn to the more general problem in which the constant $g_j$ represents the \emph{cost} of applying to $c_j$ and the student, whom we now call Ellis, has a \emph{budget} of $H$ to spend on college applications. Applying Theorem \ref{assumetzerozero}, we assume $t_0 = 0$ and disregard $c_0$ throughout.

@@

\subsection{NP-completeness}
In fact, Ellis’s problem is NP-complete, as we will show by a transformation from the binary knapsack problem, which is known to be NP-complete (Garey and Johnson 1979).

@@

\subsection{Pseudopolynomial-time dynamic program}
In this subsection, we assume, with a small loss of generality, that $g_j \in \mathbb{N}$ for $j = 1\dots m$ and $H \in\mathbb{N}$, and provide an algorithmic solution to Ellis's problem that runs in $O(Hm + m\log m)$ time and $O(Hm)$ space. The algorithm resembles a familiar dynamic programming algorithm for the binary knapsack problem (Dantzig 1957; \emph{Wikipedia}, s.v. ``Knapsack problem''). Because we cannot assume that $H \leq m$ (as was the case in Alma's problem), this represents a pseudopolynomial-time solution (Garey and Johnson 1979).

@@

\subsection{Fully polynomial-time approximation scheme}
As with the knapsack problem, Ellis's problem admits a complementary dynamic program that iterates on the value of the cheapest portfolio instead of on the cost of the most valuable portfolio. We will use this algorithm as the basis for a fully polynomial-time approximation scheme for Ellis's problem that uses $O(m^3 / \varepsilon)$ time and space. Here we assume, with a small loss of generality, that each $t_j$ is a natural number.
%Now, we modify Algorithm \ref{ellisDP2} into a fully polynomial-time approximation scheme for Ellis's problem.

@@

(Computational resources.) The bottleneck step is the creation of the lookup table in line \ref{createdlookuptable}, whose size is $O(|\mathcal{V}| m)$. Since
\begin{equation}
|\mathcal{V}| = \bar U \times 10^{P} + 1 = \bar U \times 10^ { \bigl\lceil\log_{10}\left(m ^2/ \varepsilon \bar U\right)\bigr\rceil} + 1
\leq\frac{m^2}{\varepsilon} \times \text{const.}
\end{equation}
is $O(m^2/ \varepsilon)$, the time complexity is as promised. %To prevent redundant recursive calls to $G(j, v)$, we need to record its values in a dictionary as they are computed; the space required by the dictionary is $O(|\mathcal{V}| m) = O(m^3 / \varepsilon)$.
\end{proof}

@@

\section{(WIP) Numerical experiments} \label{numericalexperiments}
In this section, we present the results of numerical experiments designed to confirm the time complexity results established above. In both experiments, markets were generated by drawing $t_j$ independently from an exponential distribution with a scale parameter of ten and rounding up to the nearest integer. To achieve partial negative correlation between $t_j$ and $f_j$, we then set $f_j = 1 / (t_j + 10 + Q)$, where $Q$ is drawn uniformly from the interval $[0, 1)$. In Experiment 1, which concerns Algorithm \ref{algorithmforlargeh}, we take each $g_j = 1$ and set $H = h = \lfloor m/ 2 \rfloor$. In Experiment 2, which concerns Algorithms \ref{ellisDP1} and \ref{ellisDP3}, each $g_j$ is drawn uniformly from the set $\{5, \dots, 10\}$ and we take $H = \lfloor \frac{1}{2} \sum g_j \rfloor$. At each combination of the experimental variables, we generated 50 markets, and each computation was repeated three times, with the fastest of the three  recorded as the computation time. Therefore, each cell of each table represents 150 computations. We report the mean and standard deviation across the 50 markets. Where applicable, we do not count the time required to sort the entries of $t$.

>>>>

% Language selector
\newif\ifen
%\enfalse % Change to false to export Korean

\ifen
{
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{conjecture}{Conjecture}
}
\else {
\newtheorem{theorem}{정리}
\newtheorem{lemma}{기본정리}
\newtheorem{corollary}{따름정리}
\newtheorem{proposition}{제의}
\theoremstyle{definition}
\newtheorem{example}{예}
\newtheorem{definition}{정의}
\newtheorem{assumption}{가정}
\newtheorem{conjecture}{추측}
}
\fi

\ifen {} \else \renewcommand*{\proofname}{증명\@}  \fi

@@

\ifen { \title{How to apply to college} }
\else {\title{How to apply to college}} \fi
\author{Max Kapur}
\date{\today}                % Activate to display a given date or no date

@@

\maketitle

\section*{Abstract}
This paper considers the maximization of the expected maximum value of a portfolio of random variables subject to a budget constraint. We refer to this as the optimal college application problem. When each variable's cost, or each college's application fee, is identical, we show that the optimal portfolios are nested in the budget constraint, yielding an exact polynomial-time algorithm. When colleges differ in their application fees, we show that the problem is NP-complete. We provide two dynamic programs for this more general setup. The first produces an exact solution in pseudopolynomial time, and the second yields a fully polynomial-time approximation scheme.

\section*{요약}
본 논문은 다수의 확률 변수로 구성된 포트폴리오의 기대 최적값을 예산 조건 하에서 최대화하는 문제를 고려한다. 이를 최적 대학 지원 문제라고 부른다. 각 확률 변수의 비용, 즉 각 대학의 지원비가 동일한 경우, 최적 포트폴리오는 예산 제약식으로 결정된 포함 사슬 관계를 가짐을 보이고 이에 따라 다항 시간 해법을 제시한다. 대학의 지원비가 서로 다른 경우, 문제가 NP-complete함을 증명한다. 일반적인 상황을 위해 두 가지 동적 계획 해법을 도출한다. 첫째는 의사 다항 시간 안에 정확한 해를 출력하며 둘째는 전체 다항 시간 근사 해법이다.

\pagebreak

\tableofcontents

\pagebreak
\ifen \section{Introduction}  \else \section{서론} \fi
\ifen This paper considers the portfolio optimization problem
\else 본 논문은 다음과 같은 최적화 문제를 고려한다.\fi
%\begin{definition}[Optimal college application portfolio] \label{generalproblemstatement}
\begin{align}
\begin{split}
\text{maximize}\quad & \operatorname{E}\Bigl[\max\bigr\{t_0,
\max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\Bigr] \\
\text{subject to}\quad & \mathcal{X} \subseteq \mathcal{C}, ~~\sum_{j\in \mathcal{X}} g_j \leq H
\end{split}
\end{align}
%\end{definition}
\ifen where $\mathcal{C} = \{ 1 \dots m\}$ is an index set, $H$ is a budget parameter, and for $j = 1 \dots m$, $g_j > 0$ is a cost parameter, $Z_j$ is a random, independent Bernoulli variable with probability $f_j$.
\else 단,  $\mathcal{C} = \{ 1 \dots m\}$은 지표 집합이며 $H$는 예산 모수이다. 각 $j = 1 \dots m$에 대해 $g_j > 0$는 비용 모수이며 $Z_j$는 확률 $f_j$를 가지는 서로 독립적인 Bernoulli 변수이다.\fi

\ifen
We refer to this problem as the \emph{optimal college application portfolio,} as follows: Consider a college market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. Finally, let $f_j$ denote her probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are probabilistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she gets into within this budget. Her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies.
\else
다음 해석에 따라 이를 `최적 대학 지원 포트폴리오 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$이다. 이 시장에 참여하는 한 학생을 고려해서 그가 $c_j$에 진학하면 $t_j$ 단위의 효용이 발생한다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그의 효용은 $t_0$이다. $c_j$의 지원비가 $g_j$이며 학생이 지원비에 쓸 수 있는 예산이 $H$라고 하자. 마지막, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성을 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 가장 좋은 학교의 기대 효용을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에 지원하는 것이다.
\fi

As Chao (2014) remarked, college application represents a somewhat subtle portfolio optimization problem. Traditional portfolio optimization models weigh the expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Meucci 2005). But college applicants maximize the observed value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the expected utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability is negatively correlated with competitiveness. That is, students  negotiate a tradeoff between highly attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet. Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Chao estimated her model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is tractable. Our study pursues a more general solution.

We take special interest in the validity of greedy solution algorithms, such as that that iteratively adds the asset that yields the greatest increase in the objective function until the budget is exhausted. Greedy algorithms produce a \emph{nested} family of solutions, parameterized by the budget $H$: If $H \leq H'$, then the greedy solution for budget $H$ is a subset of the greedy solution for budget $H'$. As Rozanov and Tamir (2020) remark, this nestedness property is useful not only for obtaining an optimal solution, but in the implementation thereof under uncertain information. For example, in the United States, many college applications are due at the beginning of November, and it is typical for students to begin working on their applications during the prior summer because colleges expect students to tailor their essays to the target school. However, students may not know how many schools they can afford to apply to until late October. The nestedness property---or equivalently, the validity of a greedy algorithm---implies that even in the absence of complete budget information, students can begin to carry out the optimal application strategy by writing essays for schools in the order that they enter the maximal portfolio.

For certain classes of optimization problems, such as maximizing a submodular set function over a cardinality constraint, a greedy algorithm is known to be a good approximate solution and exact under certain additional assumptions (Fisher et al. 1978). For other problems, notably the binary knapsack problem, the most intuitive greedy algorithm can be made to perform arbitrarily poorly (Vazirani 2001). We show analogous results for the college application problem: In the special case where each $g_j = 1$, the optimal portfolio satisfy a nestedness property that is equivalent to the validity of the greedy algorithm. This case mirrors the centralized college application process in Korea, where there is no application fee, but students are allowed to apply to only three schools during the main admissions cycle. Unfortunately, the nestedness property does not hold in the general case, nor does the greedy algorithm offers any performance guarantee. Instead, we offer a pseudopolynomial-time algorithm that is tractable for typical college market instances, as well as an approximation scheme that produces a $(1 - \varepsilon)$-optimal solution in fully polynomial time.

\ifen \subsection{Structure of this paper} \else \subsection{본 논문의 구성}\fi
Section \ref{preliminaries} introduces some additional notation and assumptions that can be imposed with trivial loss of generality.

In section \ref{homogappcosts}, we solve the special case where each $g_j = 1$ and $H$ is an integer $h \leq m$.  We show that an intuitive heuristic is in fact a $1/h$-approximation algorithm. Then, we show that the optimal portfolios are nested in the budget constraint, which yields an exact algorithm that runs in $O(hm)$-time.

@@

\pagebreak
\ifen \section{Notation and preliminary results} \else \section{표기법과 예비 결과}\fi\label{preliminaries}
Before discussing the solution algorithms, we will introduce some additional notation and a few preliminary results that will come in handy.

For the remainder of the paper, unless otherwise noted, we assume with trivial loss of generality that each $g_j \leq H$, each $f_j \in (0, 1]$, and $t_0 < t_1 \leq \cdots \leq t_m$. Below, we will show how to transform an arbitrary instance so that $t_0 = 0$, in which case each $t_j > 0$.

We refer to the set $\mathcal{X} \subseteq \mathcal{C}$ of schools to which a student applies as her \emph{application portfolio.} The expected utility the student receives from $\mathcal{X}$ is called its \emph{valuation}. %Let $x$ denote the same encoded as a binary vector, where $x_j=1 \iff j\in \mathcal{X}$ for $j=1\dots m$. 
\begin{definition}[Portfolio valuation function]
$v(\mathcal{X}) =  \operatorname{E}\left[\max\bigr\{t_0,
\max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\right]$.
\end{definition}
It is helpful to define the random variable $X  = \max\{ t_j Z_j : j \in \mathcal{X}\}$ as the utility achieved by the schools in the portfolio, so that when $t_0 = 0$, $v(\mathcal{X}) = \operatorname{E}[X]$. Similar pairs of variables with italic and script names such as $\mathcal{Y}_h$ and $Y_h$ carry an analogous meaning.

@@

\ifen \section{Homogeneous application costs}  \else \subsection{동일한 지원 비용} \fi \label{homogappcosts}
In this section, we derive a polynomial-time algorithm for the special case in which $g_j = 1$ and $H$ is a constant $h \leq m$. This case is similar to the centralized college admissions process in Korea, where there is no application fee, but by law, students are allowed to apply to no more than $h$ schools. (In the Korean case, $m=202$ and $h=3$.) Applying Theorem \ref{assumetzerozero}, we assume that $t_0 = 0$ unless otherwise noted. Throughout this section, we will call the applicant Alma, and refer to the corresponding optimization problem as Alma's problem.

@@

\ifen \subsection{Approximation properties of a na\"ive solution}  \else \subsection{Na\"ive 해법의 근사 성질} \fi
The expected utility associated with a single school $c_j$ is simply $\operatorname{E}[t_j Z_j] = t_j f_j$. It is therefore tempting to adopt the following strategy, which turns out to be inoptimal.
\begin{definition}[Na\"ive algorithm for Alma’s problem] \label{naivealgorithm}
Apply to the $h$ schools having the highest expected utility $t_j f_j$.
\end{definition}
The basic error of this algorithm is that it maximizes $\operatorname{E}\left[\sum t_j Z_j \right]$ instead of $\operatorname{E}\left[\max \{t_j Z_j\} \right]$. The latter is what Alma is truly concerned with, since in the end she can attend only one school. The following example shows that the na\"ive algorithm can produce a suboptimal solution.
\begin{example}
Suppose $m=3$, $h=2$,  $ t= (70, 80, 90) $, and $f = (0.4, 0.4, 0.3)$. 
%\implies t * f &= (28, 32, 27)
%\begin{align*}
%t &= (70, 80, 90) \\
%f &= (0.4, 0.4, 0.3) \\
%\implies t * f &= (28, 32, 27)
%\end{align*}
Then the na\"ive algorithm picks $\mathcal{T} = \{1, 2\}$ with 
$v(\mathcal{T}) = 70(0.4)(1-0.4) + 80(0.4) = 48.8$.
But $\mathcal{X} = \{2, 3\}$ with
$v(\mathcal{X}) = 80(0.4)(1-0.3) + 90(0.3) = 49.4$
is the optimal solution. 
\end{example}

@@

\begin{corollary}
The function $v(\mathcal{X})$ is not submodular. 
\end{corollary}
\begin{proof}
If $v(\mathcal{X})$ is submodular, then theorem 4.2 of Fisher et al. (1978) implies that the na\"ive algorithm achieves an optimality ratio of $v(\mathcal{T}_h) / v(\mathcal{X}_h)  \geq 1 - \left(\frac{h-1}{h}\right)^h$. Example \ref{tightexampleforoneoverhopt} provides a counterexample.
\end{proof}

@@

\ifen \subsection{The nestedness property}  \else \subsection{포함 사슬 관계 성질} \fi
It turns out that the solution to Alma's problem possesses a special structure: An optimal portfolio of size $h+1$ includes an optimal portfolio of size $h$ as a subset.
% Incl above
%To show this result, we need to introduce some new notation. For an application portfolio $\mathcal{X}$, the random variable $X  = \max\{ t_j Z_j : j \in \mathcal{X}\}$ represents the utility achieved by the portfolio, so that $v(\mathcal{X}) = \operatorname{E}[X]$.

@@

\ifen \subsection{Polynomial-time solution} \else \subsection{다항 시간 해법}\fi
Applying the result above yields an efficient algorithm for the optimal portfolio: Start with the empty set and add schools one at a time, maximizing $v(\mathcal{X}\cup \{k\})$ at each addition. Sorting $t$ is  $O(m \log m)$.  At each of the $h$ iterations, there are $O(m)$ candidates for $k$, and computing $v(\mathcal{X}\cup \{k\})$ is $O(h)$ using \eqref{closedformportfoliovaluationX}; therefore, the time complexity of this algorithm is $O(h^2 m + m \log m)$. 
%\begin{algorithm}[H] 
%  %\DontPrintSemicolon
%\caption{Optimal portfolio algorithm for Alma’s problem when $h$ is small.} \label{algorithmforsmallh}
%\KwData{Utility values $t \in[0, \infty)^m$, admissions probabilities $f \in [0, 1]^m$, application limit $h \leq m$.}
%Index schools in ascending order by $t$\;
%$\mathcal{X} \gets \O$\;
%\For{$i=1\dots h$}
%{
%    $j \gets \argmax_k\bigl\{v(\mathcal{X}\cup\{k\}) : k \notin \mathcal{X}\bigr\}$\;
%    $\mathcal{X} \gets \mathcal{X}\cup\{j\}$ \;
%}
%\Return{$\mathcal{X}$}
%\end{algorithm}
%
%\begin{theorem}[Validity of Algorithm \ref{algorithmforsmallh}]
%Algorithm \ref{algorithmforsmallh} produces an optimal application portfolio in $O(h^2 m + m \log m)$ time.
%\end{theorem}
%\begin{proof}
%Optimality follows from Theorem \ref{nestedapplication}. Sorting $t$ is  $O(m \log m)$. At each of the $h$ iterations, there are $O(m)$ candidates for $k$, and computing $v(\mathcal{X}\cup \{k\})$ is $O(h)$ using \eqref{closedformportfoliovaluationX}; therefore, the time complexity of the main loop is $O(h^2 m)$. 
%\end{proof}

@@

\ifen \subsection{Properties of the optimal portfolios} \else\subsection{최적 포트폴리오의 성질} \fi
The nestedness property implies that Alma's expected utility is a discretely concave function of $h$.

@@

\pagebreak
\ifen \section{Heterogeneous application costs} \else\section{다양한 지원 비용} \fi\label{hetappcosts}
In this section, we turn to the more general problem in which the constant $g_j$ represents the \emph{cost} of applying to $c_j$ and the student, whom we now call Ellis, has a \emph{budget} of $H$ to spend on college applications. Applying Theorem \ref{assumetzerozero}, we assume $t_0 = 0$ and disregard $c_0$ throughout.

@@

\ifen \subsection{NP-completeness} \else \subsection{NP-completeness}\fi
In fact, Ellis’s problem is NP-complete, as we will show by a transformation from the binary knapsack problem, which is known to be NP-complete (Garey and Johnson 1979).

@@

\ifen \subsection{Pseudopolynomial-time dynamic program} \else\subsection{의사 다항 시간 동적 계획} \fi
In this subsection, we assume, with a small loss of generality, that $g_j \in \mathbb{N}$ for $j = 1\dots m$ and $H \in\mathbb{N}$, and provide an algorithmic solution to Ellis's problem that runs in $O(Hm + m\log m)$ time and $O(Hm)$ space. The algorithm resembles a familiar dynamic programming algorithm for the binary knapsack problem (Dantzig 1957; \emph{Wikipedia}, s.v. ``Knapsack problem''). Because we cannot assume that $H \leq m$ (as was the case in Alma's problem), this represents a pseudopolynomial-time solution (Garey and Johnson 1979).

@@

\ifen \subsection{Fully polynomial-time approximation scheme}\else \subsection{전체 다항 시간 근사 해법}\fi
As with the knapsack problem, Ellis's problem admits a complementary dynamic program that iterates on the value of the cheapest portfolio instead of on the cost of the most valuable portfolio. We will use this algorithm as the basis for a fully polynomial-time approximation scheme for Ellis's problem that uses $O(m^3 / \varepsilon)$ time and space. Here we assume, with a small loss of generality, that each $t_j$ is a natural number.
%Now, we modify Algorithm \ref{ellisDP2} into a fully polynomial-time approximation scheme for Ellis's problem.

@@

(Computation time.) The bottleneck step is the creation of the lookup table in line \ref{createdlookuptable}, whose size is $O(|\mathcal{V}| m)$. Since
\begin{equation}
|\mathcal{V}| = \bar U \times 10^{P} + 1 = \bar U \times 10^ { \bigl\lceil\log_{10}\left(m ^2/ \varepsilon \bar U\right)\bigr\rceil} + 1
\leq\frac{m^2}{\varepsilon} \times \text{const.}
\end{equation}
is $O(m^2/ \varepsilon)$, the time complexity is as promised. %To prevent redundant recursive calls to $G(j, v)$, we need to record its values in a dictionary as they are computed; the space required by the dictionary is $O(|\mathcal{V}| m) = O(m^3 / \varepsilon)$.
\end{proof}

@@

\pagebreak
\ifen \section{(WIP) Numerical experiments} \else \section{계산적 실험}\fi\label{numericalexperiments}
In this section, we present the results of numerical experiments designed to confirm the time complexity results established above. In both experiments, markets were generated by drawing $t_j$ independently from an exponential distribution with a scale parameter of ten and rounding up to the nearest integer. To achieve partial negative correlation between $t_j$ and $f_j$, we then set $f_j = 1 / (t_j + 10 Q)$, where $Q$ is drawn uniformly from the interval $[0, 1)$. In Experiment 1, which concerns Algorithm \ref{algorithmforlargeh}, we take each $g_j = 1$ and set $H = h = \lfloor m/ 2 \rfloor$. In Experiment 2, which concerns Algorithms \ref{ellisDP1} and \ref{ellisDP3}, each $g_j$ is drawn uniformly from the set $\{5, \dots, 10\}$ and we take $H = \lfloor \frac{1}{2} \sum g_j \rfloor$. At each combination of the experimental variables, we generated 50 markets, and each computation was repeated three times, with the fastest of the three  recorded as the computation time. Therefore, each cell of each table represents 150 computations. We report the mean and standard deviation across the 50 markets. Where applicable, we do not count the time required to sort the entries of $t$.
